# RplotterPkg Examples

The goal of RplotterPkg is to provide easy access to the many ggplot2 geom plotting routines for everyday use.  The package uses a functional approach along with the fast, efficient data frame processing from [`data.table`](https://github.com/Rdatatable/data.table "data.table github").

## Installation

You can install the development version of RplotterPkg from [GitHub](https://github.com/) with:

Using `pak::pak()`:

`pak::pak("deandevl/RplotterPkg")`

Using `devtools::install_github()`:

`devtools::install_github("deandevl/RplotterPkg")`

## Setup

Let's load the required R script libraries from CRAN and github:

### Load the required R packages from CRAN:

```{r}
#| warning: false
#| message: false

library(data.table)
library(ggplot2)
library(RColorBrewer)
library(aplpack)
```

### Load the required R package from GitHub:

```{r}
#| warning: false
#| message: false

devtools::install_github("deandevl/RplotterPkg")
```


## Standard Plotting

RplotterPkg offers many of the standard plotting such as scatter, box, density, histogram, range, heatmap, and stick plots. The following example shows how easy it is assign x/y axis variables and label for a heatmap.

```{r}
#| fig-width: 11
#| fig-height: 7
#| fig-cap: "Rplotter::create_heatmap example"


RplotterPkg::create_heatmap(
    df = RplotterPkg::spinrates,
    aes_x = "velocity",
    aes_y = "spinrate",
    aes_fill = "swing_miss",
    aes_label = "swing_miss",
    label_fontface = "bold",
    title = "Likelihood of swinging and missing on a fastball",
    x_title = "Velocity",
    y_title = "Spinrate",
    rot_y_tic_label = TRUE
  ) +
  ggplot2::scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"),
    n.breaks = 8
  ) 
```

## Additional Plotting

Also included with RplotterPkg are routines that are not always available such as spread_level, symmetry, stem_leaf, waffle, and multi-paneled plots.  In the examples below we have a waffle plot of simple proportions and a stem_leaf plot comparing women Boston marathon times by age groups.

```{r}
#| fig-width: 11.5
#| fig-height: 8
#| fig-cap: "RplotterPkg::create_waffle_chart example"


proportions_v <- c(
  var1=10, var2=40, var3=20, var4=50, var5=5,
  var6=30, var7=10, var8=67, var9=42, var10=33,
  var11=7, var12=35, var13=22, var14=90, var15=43
)

RplotterPkg::create_waffle_chart(
  x = proportions_v,
  title = "Test For 15 Proportion Variables",
  cell_color = "white",
  cell_fill = "brown",
  cell_nonfill = "lightgray",
  cell_alpha = 0.5,
  line_width = 4
)
```

```{r}
#| fig-cap: "RplotterPkg::stem_leaf_display example"
#| fig-height: 5.5

# stem and leaf for marathon times of women across ages
marathon_times_lst <- list(
  "age_20" = RplotterPkg::boston_marathon[age == 20,]$time,
  "age_30" = RplotterPkg::boston_marathon[age == 30,]$time,
  "age_40" = RplotterPkg::boston_marathon[age == 40,]$time,
  "age_50" = RplotterPkg::boston_marathon[age == 50,]$time,
  "age_60" = RplotterPkg::boston_marathon[age == 60,]$time
)
# display stem and leaf of women times across ages
table_grob <- RplotterPkg::stem_leaf_display(
  x = marathon_times_lst,
  title = "Women times(min) in Boston marathon",
  heading_color = "#FF5500",
  display_grob = FALSE
)
grid::grid.newpage()
grid::grid.draw(table_grob)
```


